Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-10 paper/paper.tex
edits

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a ReferenceError. Also, updating the other engines to use WScript would
require a non-trivial manual process.}

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.

For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios. Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}.

>>>>

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use the default
well-known assertions available in JS, which the other JS engines use.
Instead, it uses its own testing framework, WScript. In this case, we could
not easily reproduce the \chakra unit tests in the other engines since it would
raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
require a non-trivial manual process. This is why \chakra is not showed
in Table~\ref{tab:test-suites}.}

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.
\Fix{For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios.
We performed seven consecutive executions because,
since the studied JS engines release new versions on a daily basis,
we wanted to make sure if the failing tests raised by the Test262 suite
were rapidly fixed by the maintenance team. If these errors were quickly
fixed, that would suggest that this given engine would be aligned with
the ECMAScript specification.}
Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}.
